% \documentclass[english]{article}
% \usepackage[T1]{fontenc}
% \usepackage[latin9]{inputenc}
% \usepackage{amsmath}
% \usepackage{amssymb}
% \usepackage{babel}
% \usepackage{subfiles}
\documentclass[master.tex]{subfiles}
\begin{document}

    STRIPS(Standford instritute research problem solver) is schema used
    to define a domain and a problem.

    STRIPS contain four components
    \begin{itemize}
    \item An initial state $I$
    \item A set of conditions P which contain all possible predicates
    \item A goal state $G$
    \item A set $O$ of all available actionschemas
    \end{itemize}
    Actionschemas in STRIPS are defined as $\text{\ensuremath{\left(P^{+},P^{-},E^{+},E^{-}\right)}}$.
    Futhermore, an actionschema also contain a list of variable $(x_{1},x_{2},\dots,x_{n-1},x_{n})$
    which are the input parameters for an action. The preconditions define
    when an actions is invalid meaning it can not be used, and the postconditions
    define what predicates are present/not present in the state after
    it has been applied. Predicates in the pre/post- conditins of an actionschema
    are ungrounded meaning the object which they refer to are variables
    and can change dependent on the input to an action.

    To apply an action to a state all predicates in an action must be
    grounded. To ground a predicate $p(x_{1},\dots,x_{n})$ a mapping
    $M$ from the variables to the real objects in the environment is
    required, for instance $\{x_{1}\mapsto red,x_{2}\mapsto blue.....\}$.
    The mapping is then applied to the variables of the predicate, after
    which the predicate is considered grounded. Thus we define the grouding
    as a function $g:p(x_{1},\dots,x_{n})\mapsto p\left(M\left(x_{1}\right),,\dots,M\left(x_{n}\right)\right)$.

    After predicates in an action has been grounded the preconditions
    are checked if they hold for the current state $s$., \\
    \[
    g\left[P^{+}\right]\subseteq s\,\land\, g\left[P^{-}\right]\cap s=\emptyset
    \]
    .

    If they hold then the postconditions can be applied to the state to
    form the new state $s'$.

    \[
    s'=\left(s\setminus g\left[E^{-}\right]\right)\cup g\left[E^{+}\right]
    \]


    grounded predicates that are identical and reside in both $E^{+}$
    and $E^{-}$ are called spurious effects, if they are ignored the
    then because of the definition of $s'$ then the positive effects
    in $E^{+}$will always take precedence.

    Thus a state transition is defined as $(s,a,s')$ where $s$ is the
    current state, $a$ is the grounded action and $s'$ is the new state.
    Lastly it is important to note that all actions in STRIPS are absolute,
    meaning they contain no conditional effects.

\section{Effects}
\subfile{TransitionLearning/Effects}

\section{Preconditions}
\subfile{TransitionLearning/Preconditions}

\section{Conditional Effects}
\subfile{TransitionLearning/Conditionals}

\end{document}
