\documentclass[../Master.tex]{subfiles}
\providecommand{\master}{..}
\begin{document}

Consider again a state transition $\left( s, a, s' \right)$. The hypergraph constructed for $\ts(s)$ (as shown above) now describes how the predicates in $s$ are interconnected without mentioning specific objects or variables. Similarly, a single effect $p$ of action $a$ can be encoded as a hypergraph by the function $hypergraph(p,\ts(s))$, which constructs a hypergraph for $\ts(s) \cup \{p\}$, labelling the predicate edge describing $p$ as an effect.

Such a hypergraph describes which bindings were present in $\ts(s)$ when the effect $p$ occurred, and how $p$ is connected to them. In other words, it denotes the preconditions for the conditional that spawned $p$ which has not been disproven, and any binding \textit{not} in the hypergraph is disproven to be a precondition.

\begin{proposition}\label{prop:ca:disprovenHg}
    For a state transition $\left( S, a, S' \right)$ and a predicate $p \in \Delta S$, any binding absent from $hypergraph \left( p, X(S) \right)$ is not a precondition for the conditional in $A$ with $p$ as effect. 
\end{proposition}

\begin{proof}[Proof by contradiction]
    Consider a state transition $\left( S, a, S' \right)$, a predicate $p \left( o_1 \right) \in \Delta S$, and the hypergraph $H = hypergraph\left( p\left(o_1\right), X(S) \right)$. If a binding $(p_1, q_1)$ is not present in $H$ (meaning that there is no binding edge in $H$ containing $p_1$ and $q_1$), then that binding is not present in $X(S)$ (i.e.\ $q\left(o_1\right) \notin S$). Thus, if that binding was a precondition for the conditional that spawned $p\left(o_1\right)$, then that interpretation of the conditional would have failed, and $p\left( o_1 \right)$ would not have occurred in $\Delta S$. Additionally, by Proposition~\ref{prop:ca:singleConditional}, no other conditional in $A$ could have caused the effect $p \left(o_1\right)$.
\end{proof}

Recall that any two predicates $p$ and $q$ in $\Delta S$ with the same name are effects of the same conditional (by Proposition~\ref{prop:ca:singleConditional}), and that any bindings absent from \textit{either} of the hypergraphs $H_p = hypergraph(p, X(S))$ and $H_q = hypergraph(q, X(S))$ are disproven to be preconditions of that conditional (by Proposition~\ref{prop:ca:disprovenHg}). Consequently, if the two hypergraphs can be merged into one hypergraph $H'$, such that $H'$ only contains bindings that $H_p$ and $H_q$ has in common, then any binding absent from $H'$ can not be a precondition for the conditional either. 

In the following, we will assume availability of such a merging function (denoted $merge$), and a detailed algorithm can be found in Section~\ref{sec:C:HGMerging}.

From the above, it follows that all grounded predicates with name $n$ in $\Delta\left(s, s'\right)$ can be merged together to disprove preconditions of the conditional that spawned them. The resulting hypergraph then constitutes all bindings that have not explicitly been disproven to be predicates, and can as such be reused in another transition. As such, this hypergraph describes the unknown knowledge $U$.

As with connecting paths, we have the concept of candidates, i.e.\ reasons a conditional could have failed in a certain interpretation. Recall that such a reason is a connecting path that was not present in the failing state. Since vertices in a hypergraph can be uniquely identified, and paths to the effect can be described by a binding to another vertex that is itself transitively connected, a candidate for failure can be encoded as a tuple of two vertices. I.e.\ it is sufficient to record the last component of the offending connecting path.

Similarly to nonconditional actions and connection paths, a candidate is proven to be a precondition if the candidate set it is part of is reduced to the singleton set. Such a reduction can be accomplished by removing tuples from a candidate set if there is no binding edge in $U$ containing both vertices of the tuple. Given a set $c$ of vertex tuples and the set of binding edges from $U$, the $reduce$ function removes candidates from $c$ as described above.

\begin{equation*}
    reduce(c, E_B) =
    \left\{ \left( t_1, t_2 \right) \mid 
        \left( t_1, t_2 \right) \in c \land 
        \exists_{b \in E_B} \left[ t_1 \in b \land t_2 \in b \right] 
    \right\}
\end{equation*}

As each vertex in a hypergraph has unique identifiers, and identifiers for two hypergraphs are not necessarily identical, the $merge$ function must also perform an identifier renaming. Thus, the $reduce$ function ascribed above will not work, as the vertex identifiers will not match, and vertices in $U$ can not be matched with those in $K$. Therefore, $merge$ should return the renaming function used, so that it can be applied to $C$ and $K$.

As described in the next section, a vertex may have been ``shadowing'' another, such that what we perceived as a single vertex in a binding edge in $U$ were in fact two. If that is the case, the renaming function will replace that vertex with two equally-named vertices with different identfiers, both part of the binding edge the original vertex was part of. 

Thus, when this renaming is applied to a candidate tuple $(u,v)$, it produces $|rn(u)| \times |rn(v)|$ tuples, which replaces $(u,v)$ in the candidate set, i.e.\ 

\begin{equation*}
    rnCands(c, rn) =
    \left\{ 
        \left( u', v' \right) \mid 
        (u, v) \in c \land u' \in r(u) \land v' \in r(v) 
    \right\}
\end{equation*}

When the renaming is applied to a vertex $v \in K$, then it holds that if $|rn(v)| > 1$, neither of the vertices in $rn(v)$ are proven. \texttt{Explain}.

\begin{algorithm}
    \caption{Algorithm for learning conditional effects using hypergraphs}\label{algo:CondEffLearn}
    \begin{algorithmic}
        \Function{Update-Knowledge}{$n$, $\Delta s$, $U$, $K$, $C$}
            \ForAll{predicates $p \in \Delta s$ with name $n$}
                \State{$H_p \gets hypergraph(p, s)$}
                \State{$\left(U, r \right) \gets merge \left( U, H_p \right)$}
                \State{$\left( C, K \right) \gets rename(r, C, K)$}
                % \State{$C \gets \left\{ rnCands(c, rn) \mid c \in C \right\}$}
                % \State{$K \gets rnKnown(K, rn) $}
            \EndFor
            \ForAll{predicates $q \notin \Delta s$ with name $n$}
                \State{$H_q \gets hypergraph(q, s)$}
                \State{$C \gets C \cup cands\left( H_q, U \right)$}
            \EndFor
            \State{$C = \left\{ reduce\left(c, U\right) \mid c \in C \right\}$}
            \State{Remove any singleton sets from $C$, and add them to $K$}
        \EndFunction

        \Function{$\textsc{Conditional-Effect-Learn}$} {$\left( s, a, s'\right)$, $U$, $K$, $C$}
            \ForAll{predicate names $n$}
                \State{$\left(U_n, K_n, C_n\right) = UpdateKnowledge\left(n, \Delta s, U_n, K_n, C_n \right)$}
            \EndFor
            \State\Return{$\left( U, K, C\right)$}
        \EndFunction%
    \end{algorithmic}
\end{algorithm}

\end{document}
